The Pair Distribution Function of the Inhomogeneous Hard-Sphere Fluid

### 2013-10-19 papers/pair-correlation/paper.tex
make pair-correlation figures more consistent and readable in b/w Tested on bingley. Took 2:09.61.
add square-well da1dz plot (currently broken) Tested on darcy. Took 0:22.33.
beautify dadz plots a bit more Tested on darcy. Took 0:28.35.
add text to results section of pair paper Tested on collins. Took 0:35.50.

\newcommand{\fixme}[1]{\text{\red{[#1]}}}

@@

\begin{document}
\title{Using Fundamental Measure Theory to treat the Pair
  Distribution Function of the Inhomogeneous Hard-Sphere Fluid}

@@

\section{Results}
\subsection{Pair distribution function}

@@

@@

\begin{figure}
  \includegraphics[width=\columnwidth]{figs/pair-correlation-pretty-2.pdf}
  \caption{\paircaption{0.2}}\label{fig:pair-distribution-2}
\end{figure}
\begin{figure}
  \includegraphics[width=\columnwidth]{figs/pair-correlation-pretty-3.pdf}
  \caption{\paircaption{0.3}}\label{fig:pair-distribution-3}
\end{figure}
\begin{figure}
  \includegraphics[width=\columnwidth]{figs/pair-correlation-pretty-4.pdf}
  \caption{\paircaption{0.4}}\label{fig:pair-distribution-4}
\end{figure}

Discuss the pair distribution function here, explaining plots
  and discussing results and comparison.

@@

\begin{figure}
  \includegraphics[width=3cm]{figs/dadz-3-2.pdf}
  \includegraphics[width=3cm]{figs/dadz-3-3.pdf}
  \includegraphics[width=3cm]{figs/dadz-2-2.pdf}
  \includegraphics[width=3cm]{figs/dadz-2-3.pdf}
  %%\includegraphics[width=3cm]{figs/dadz-4-3}
  \caption{Plot of $\frac{da_1}{dz}$ near a hard
    wall. For what $\Phi$?}\label{fig:dadz}
\end{figure}

>>>>

\newcommand{\fixme}[1]{\red{[#1]}}

@@

\begin{document}
\title{The Pair Distribution Function of the Inhomogeneous Hard-Sphere
  Fluid}

@@

@@

\section{Results}

@@

\subsection{Pair distribution function}

%% \begin{figure}
%%   \includegraphics[width=\columnwidth]{figs/pair-correlation-pretty-2.pdf}
%%   \caption{\paircaption{0.2}}\label{fig:pair-distribution-2}
%% \end{figure}
\begin{figure}
  \includegraphics[width=\columnwidth]{figs/pair-correlation-pretty-3.pdf}
  \caption{\paircaption{0.3}}\label{fig:pair-distribution-3}
\end{figure}
%% \begin{figure}
%%   \includegraphics[width=\columnwidth]{figs/pair-correlation-pretty-4.pdf}
%%   \caption{\paircaption{0.4}}\label{fig:pair-distribution-4}
%% \end{figure}

We begin by examining the pair distribution function near a hard wall,
with a focus on the case where one of the two spheres is in contact
with the hard wall.  Figure~\ref{fig:pair-distribution-1}a
and~\ref{fig:pair-distribution-3}a compare the results of our
approximate functional with Monte Carlo simulation at packing
fractions of 0.1 and 0.3 respectively.  We see reasonable agreement at
the lower density, with some reduced oscillations at larger distances,
and a flatter angular dependence when the two spheres are in contact.
At the higher density, we see significant structure developing in the
simulation results that is not reflected in our approximation.

Figure~\ref{fig:pair-distribution-1}b
and~\ref{fig:pair-distribution-3}b show the pair distribution function
as plotted along a path illustrated in
Fig.~\ref{fig:pair-distribution-1}a.  These plots compare this work
with Monte Carlo results, as well as the approximations of Sokolowski
and Fischer~\cite{sokolowski1992role} and that of Fischer and
Methfessel~\cite{fischer1980born} at packing fractions of 0.1 and 0.3.
The approach of Fischer and Methfessel is only valid when the two
spheres are in contact, and is therefore only plotted on that segment
of the path.  As an input to both previous approximations we use the
hard sphere radial distribution function found using Monte Carlo
simulation, interpolated as necessary.  We find that both previous
approximations to the pair distribution function predict the
qualtitative angular dependence of the pair distribution function at
contact better than this work.  However, in each case the pair
distribution function has a systematic error at contact---either too
high or too low.  Thus while our approximation is smoother than either
of the existing approaches, its errors will have a tendancy to cancel
when used in a perturbation expansion.  At higher densities, the
approximation of Fischer and Methfessel requires evaluating the radial
distribution function at densities significantly higher than the
freezing density, which poses numerical difficulties when using the
radial distribution function from simulation.  When the two points are
more than a radius away from contact, we find that any of these
approaches gives a reasonable prediction, with our approach
underestimating the oscillations in $g^(2)$, as expected based on our
fit in Fig.~\ref{fig:radial-distribution}.

@@

\begin{figure}
  \includegraphics[width=\columnwidth]{figs/dadz-3-2.pdf}
  %\includegraphics[width=\columnwidth]{figs/dadz-3-3.pdf}
  \includegraphics[width=\columnwidth]{figs/dadz-2-2.pdf}
  \includegraphics[width=\columnwidth]{figs/dadz-square-well-3.pdf}
  %%\includegraphics[width=3cm]{figs/dadz-4-3}
  \caption{Plot of $\frac{da_1}{dz}$ near a hard
    wall. For what $\Phi$?}\label{fig:dadz}
\end{figure}
